{{< var titll >}}

### 2024-07-13 presentation.qmd
updpres

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(huxtable)
library(kableExtra)
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
appnf <- seloutput(rppnf <- selreport(basc))
appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(penf)`$
\end{equation*}

Election outome 
```{r, echo=F}
round(polynom::integral(penf,c(0,1)),3)
```

@@

$f(x)_{0}^{1}=`r paste0(per1)`$

@@

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
appnf <- seloutput(rppnf <- selreport(basc))
appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))

round(polynom::integral(penf,c(0,1)),3)

per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(penf,3))`$
\end{equation*}

Election outome 
  - Integral `r round(polynom::integral(penf,c(0,1)),3)`
  - Counting `r round(rppnf[[1]]$desms[7,2],3)`

@@

\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(per1,3))`$
\end{equation*}

@@

- Venezuela referendum to recall President Hugo Chávez (2004)
	- Mode 1: Computerized Voting Centers
	- Mode 2: Manuel Voting Centers

> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.

![](images/manifold.png){width=300}
